Generative Synthesis of Insurance Datasets

### 2020-06-19 manuscript/manuscript.Rmd
resize figs

```{r distribution-area, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Distributions of the Area variable.", fig.width=6, fig.height=2}
make_bar(combined, "area")
```

```{r distribution-bonus-malus, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Distributions of the Bonus/Malus variable.", fig.width=6, fig.height=2}
make_histogram(combined, "bonus_malus")
```

```{r distribution-region, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Distributions of the Region variable.", fig.width=6, fig.height=2}
make_bar(combined, "region")
```

@@

```{r relativities-area, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Relativities of the Area  variable across cross-validated models", fig.width=6,fig.height=2}
coefs %>% 
  filter(!is.na(level)) %>% 
  filter(variable == "area") %>% 
  ggplot(aes(x = level, y = relativity, color = dataset)) +
  geom_boxplot() +
  theme_bw() +
  geom_hline(yintercept = 1, linetype = "dashed", color = "red")
```

```{r relativities-bonus-malus, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Relativities of the Bonus/Malus  variable across cross-validated models", fig.width=6,fig.height=2}
coefs %>% 
  filter(is.na(level)) %>% 
  filter(variable == "bonus_malus") %>% 
  ggplot(aes(y = relativity, x = level, color = dataset)) +
  theme_bw() +
  geom_boxplot() +
  theme(axis.title.x=element_blank(),
       axis.text.x=element_blank(),
       axis.ticks.x=element_blank()) +
  geom_hline(yintercept = 1, linetype = "dashed", color = "red")
```

```{r relativities-region, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Relativities of the Region  variable across cross-validated models", fig.width=6,fig.height=2}
coefs %>% 
  filter(!is.na(level)) %>% 
  filter(variable == "region") %>% 
  ggplot(aes(x = level, y = relativity, color = dataset)) +
  geom_boxplot() +
  theme_bw() +
  geom_hline(yintercept = 1, linetype = "dashed", color = "red") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

>>>>

```{r distribution-area, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Distributions of the Area variable.", fig.width=6, fig.height=1.65}
make_bar(combined, "area")
```

```{r distribution-bonus-malus, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Distributions of the Bonus/Malus variable.", fig.width=6, fig.height=1.65}
make_histogram(combined, "bonus_malus")
```

```{r distribution-region, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Distributions of the Region variable.", fig.width=6, fig.height=1.65}
make_bar(combined, "region")
```

@@

```{r relativities-area, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Relativities of the Area  variable across cross-validated models", fig.width=6,fig.height=1.65}
coefs %>% 
  filter(!is.na(level)) %>% 
  filter(variable == "area") %>% 
  ggplot(aes(x = level, y = relativity, color = dataset)) +
  geom_boxplot() +
  theme_bw() +
  geom_hline(yintercept = 1, linetype = "dashed", color = "red")
```

```{r relativities-bonus-malus, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Relativities of the Bonus/Malus  variable across cross-validated models", fig.width=6,fig.height=1.2}
coefs %>% 
  filter(is.na(level)) %>% 
  filter(variable == "bonus_malus") %>% 
  ggplot(aes(y = relativity, x = level, color = dataset)) +
  theme_bw() +
  geom_boxplot() +
  theme(axis.title.x=element_blank(),
       axis.text.x=element_blank(),
       axis.ticks.x=element_blank()) +
  geom_hline(yintercept = 1, linetype = "dashed", color = "red")
```

```{r relativities-region, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Relativities of the Region  variable across cross-validated models", fig.width=6,fig.height=1.65}
coefs %>% 
  filter(!is.na(level)) %>% 
  filter(variable == "region") %>% 
  ggplot(aes(x = level, y = relativity, color = dataset)) +
  geom_boxplot() +
  theme_bw() +
  geom_hline(yintercept = 1, linetype = "dashed", color = "red") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
